\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-04-24 paper/main.tex
Refined some sentences according to reviews

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build (release or nightly), and column
``environment'' shows the breakdown of instances for each kind of
environment to reproduce the bug (venv or docker). Co-incidentally,
all bugs that require a GPU build are reproduced using a docker
container, i.e. the column venv-docker matches would have been
observed with a column CPU-GPU, to indicate if the bug is can be
reproduced with a CPU or if it requires a
GPU. Table~\ref{table:bug-stats} shows the breakdown error types for
the bugs in our dataset. The row ``Incorrect Output'' is listed first
as it requires a distinct kind of oracle comparing consistency of the
outputs of test runs on a CPU and on GPU. In total, we have
\numbugtypes\ different types of bug manifestations across the three
libraries.

@@

The following script runs FreeFuzz all bugs associated with version
2.2.0 of \torch.  The command \CodeIn{run-tool} takes the library
version as an input, along with the name of the docker container
(already created), the name of the library, and the user-provided
script containing the commands to run the tool
(\CodeIn{run\_freefuzz\_docker.sh}. The script reports on output how
many bugs are reproducible with this library version were successfully
reproduced by the given tool.  Tool execution proceeds as
follows. First, a Docker container associated with the tool is created using
\CodeIn{install\_freefuzz\_docker.sh}. Next, a reproducible bug is tested using
the specified library version as input to verify the setup.
Following this, the preprocessing script (\CodeIn{preprocess.py}) is executed 
to extract error types and identify buggy APIs for the given library version.
The environment inside the Docker container is then updated to match the specified version, 
ensuring compatibility before running the fuzzing tool. Once execution is complete, a postprocessing 
script (\CodeIn{postprocess.py}) is run to analyze the execution log against the ground truth, 
determining whether the bugs were successfully reproduced.

>>>>

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
for each kind of build (release or nightly), and column
``environment'' shows the breakdown of instances for each kind of
environment to reproduce the bug (venv or docker). Co-incidentally,
all bugs that require a GPU are reproduced using docker
containers, i.e. the column venv-docker matches what would have been
observed with a column CPU-GPU, to indicate if the bug can be
reproduced with a CPU or if it requires a
GPU. Table~\ref{table:bug-stats} shows the breakdown error types for
the bugs in our dataset. The row ``Incorrect Output'' is listed first
as it requires a distinct kind of oracle comparing consistency of the
outputs of test runs on a CPU and on GPU. In total, we have
\numbugtypes\ different types of bug manifestations across the three
libraries.

@@

The following script runs FreeFuzz on all bugs associated with version
2.2.0 of \torch.  The command \CodeIn{run-tool} takes the library
version as an input, along with the name of the docker container
(already created), the name of the library, and the user-provided
script containing the commands to run the tool
(\CodeIn{run\_freefuzz\_docker.sh}. The script reports how
many bugs that are reproducible with this version of the library were successfully
reproduced by the given tool.  Tool execution proceeds as
follows. First, a Docker container associated with the tool is created using
\CodeIn{install\_freefuzz\_docker.sh}. Next, a reproducible bug is tested using
the specified library version as input to verify the setup.
Following this, the preprocessing script (\CodeIn{preprocess.py}) is executed 
to extract error types and identify buggy APIs for the given library version.
The environment inside the Docker container is then updated to match the specified version, 
ensuring compatibility before running the fuzzing tool. Once execution is complete, a postprocessing 
script (\CodeIn{postprocess.py}) is run to analyze the execution log against the ground truth, 
determining whether the bugs were successfully reproduced.
